\documentclass[10pt,a4paper,notitlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{tgpagella}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{enumitem}
\author{Jehan Singh}
\title{Curriculum Vitae}

\hypersetup{colorlinks, urlcolor=blue}

\begin{document}

\section*{%
\begin{Huge}
Jehan Singh\
\end{Huge}\\
Curriculum Vitae}

\hrulefill

\section*{Personal Details}

\begin{itemize}[noitemsep]
	\setlength\itemsep{0.02em}
    \item Name: Jehan Singh
    \item Email: \href{mailto:jehansingh.97@gmail.com}{jehansingh.97@gmail.com}
\end{itemize}

\section*{Personal Profile}

I am an electrical and computer engineering graduate currently working in the field of embedded
systems and automation. I am presently working towards a masters degree in nanoelectronics at the
University of Johannesburg, with a focus on graphene manufacturing processes for biosensors. I am
eager to expand my skills. I am interested in general electronic design, particularly embedded
system design, and I have several years of experience and academic training in  working with Linux
systems, on desktops, embedded devices, and with high performance computing clusters. I can
effectively combine these skills to take on problems ranging from automation to testing to hardware
debugging, allowing me to provide effective solutions to problems.

\section*{Work Experience and Notable Projects}

\subsection*{Junior Embedded Systems Engineer at Enspara: 2020-present}
\begin{itemize}[noitemsep]
	\setlength\itemsep{0.02em}
    \item Developed monitoring and control solutions for reducing the energy consumption of industrial and commercial equipment
    \item Maintained and upgraded existing hardware and software including a custom embedded Linux image used on monitoring hardware
    \item Wrote documentation and manuals for hardware installations and software deployment
    \item Operated independently to perform design and maintenance tasks on company IoT fleet
    \item Tools used: nodejs, node-red, python, bash, bitbake build system, git, AWS Things, Siemens PLC.
\end{itemize}

\subsection*{Winning Student Cluster Competition ISC 2019}
\begin{itemize}[noitemsep]
	\setlength\itemsep{0.02em}
    \item Competed in and won the ISC Student Cluster Competition 2019 as part of a team on behalf of the Centre for Scientific and Industrial Research
    \item Placed first out of 14 teams: \href{https://www.chpc.ac.za/index.php/news2/241-south-africa-wins-international-student-cluster-competition-for-the-fourth-time}{News Article}
    \item Designed, prepared, optimized and ran benchmarks and applications on a six-node, 336 core CentOS cluster.
    \item Underwent mentorship from the South African Centre for High Performance Computing as well
        as several days of learning from Dell and TACC Engineers.
    \item Built and optimized libraries for OpenMPI, HDF5, FFTW, PARMETIS and GSL using open source compilers and Intel Parallel Studio.
    \item Primary focus was on optimizing the SwiftSim Astrodynamics package and assisted in optimization for HPL, HPCC, HPCG, and OpenFOAM.
    \item Wrote scripts in bash and python to monitor and control the performance of the cluster. 
    \item Reference: David Macleod \href{mailto:dmacleod@csir.co.za}{dmacleod@csir.co.za}
\end{itemize}

\subsection*{Penguin Data Collection Project 2018-2019}
\begin{itemize}[noitemsep]
	\setlength\itemsep{0.02em}
    \item Designed, programmed and integrated an embedded Linux based system for collecting images,
        RFID scans, and weight readings of endangered penguins on St. Croix Island.
    \item Developed python software which must be robust enough to run unchecked for up to six months and recover from failures.
    \item Integrated and adapted system hardware and software to survive harsh conditions and support other research goals.
    \item This was my undergraduate final project, my report and poster can be found \href{https://awful.cloud/upl/thesis.pdf}{here} and \href{https://awful.cloud/upl/poster.pdf}{here}.
    \item Reference: Justin Pead: \href{mailto:justin.pead@uct.ac.za}{justin.pead@uct.ac.za}
\end{itemize}

\section*{Education}
\begin{itemize}[noitemsep]
	\setlength\itemsep{0.02em}
    \item 2021-present: Studying part-time towards a Masters of Science in Engineering in Micro and Nanoelectronics at the University of Johannesburg, with a research focus on graphene manufacturing processes for nanobiosensors.
    \item 2016-2020: Graduated with a Bachelor of Science in Engineering in Electrical and Computer Engineering from the University of Cape Town
    \item 2015: Graduated from Northcliff High School with 5 distinctions.
\end{itemize}

\subsection*{Undergraduate Vacation Work}
\begin{spacing}{1.1}
\textbf{Software intern at ABSA Aliens, 2018}\\
Two-week placement, where I developed an Android app alongside two other students implementing an
infrastructure-free local positioning system using existing wi-fi networks. 
    \vspace*{0.5em}\\
\textbf{Security intern at MWR Information Security, 2017}\\
Two-week training in webapp security, penetration testing with industry standard rools, and security
best practices, including incident reporting skills.
    \vspace*{0.5em}\\
\textbf{Software intern at Journeyapps Stellenbosch, 2017}\\
Three-week internship where I implemented a NodeJS API server which converted existing REST API's
into GraphQL API's according to an XML API schema.
\end{spacing}

\section*{Skills}
\begin{itemize}[noitemsep]
	\setlength\itemsep{0.02em}
    \item Experience using the programming languages and tools Python (including scientific computing packages), NodeJS, Lua, Pascal, and Linux Shell Scripting tools.
    \item Experience with Linux system administration and environment management across a variety of distributions and environments, including Linux cluster environments and web servers
    \item Experience operating, monitoring and tuning massively parallely HPC computing environments
    \item Significant experience with GNU/Linux Operating Systems on server, desktop and embedded environments
    \item Elementary or Basic knowledge of C, Perl, Java, including some Android development, HTML, CSS, and SQL
    \item Elementary skill with VLSI layout, 3D CAD in Inventor, SolidWorks, and FreeCAD, PCB layout, and SPICE simulation
    \item Elementary skill with Ansible, SLURM, Grafana, Ganglia, and Lmod automation and management tools
    \item Competent user of both Microsoft Office programs and LaTeX document creation tools
    \item Experience with electronic design including practical lab testing, soldering and wiring
    \item Capable of quickly learning about new tools or systems as needed
    \item Skill at working with technical equipment or documents and software manuals
\end{itemize}

\end{document}
